### 2018-10-15 Manuscript/Manuscript.tex

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/LIP_Map.pdf}
	\caption{\textbf{Map of current extent of lithologies associated with LIPs that erupted between 520 Ma and the present (shown in orange) as well as the estimates of the initial LIP area used in the area analysis (shown in blue and slightly modified from \citealp{Ernst2017a}).}}
	\label{fig:LIP_map}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{LIP preservation through time. The ratio of estimates of the present-day area to that of the original area are shown for 17 basaltic LIPs. The best-fit exponential function to these data is shown which has a half-life of 36 Myr.}}
	\label{fig:LIP_preservation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A) paleolatitude of emplacement and the initial area estimate of each LIP in the compilation.
    B) total LIP area through time for the different post-emplacement models.
    C) tropical LIP area through time for the different post-emplacement models.
    D) heat map for one of the models showing the latitudinal distribution of LIP area.
    E) latitudinal extent away from the poles of land ice through time.}}
	\label{fig:LIP_area}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation_cropped.pdf}
	\caption{\textbf{The overlap and correlation values for various LIP post-emplacement scenarios are shown with circles (d1 : LIP decay with half-life of 36 Myr; d2: LIP decay with half-life of 120 Myr; b1: 50$\%$ burial of LIPs associated with rifting; b2: 100$\%$ burial of LIPs associated with rifting). These values are compared to histograms that are range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The only scenario for which there is a positive correlation coefficient related to ice extent and LIP area is that of a relatively slow decay rate (d2) and complete burial of LIPs associated with rifting (b2). This positive correlation is weak (\textit{r}=0.10) and is not significant as randomly timed glacial intervals correlate better than the record 28$\%$ of the time. With an associated p-value of 0.28, the null hypothesis that glacial intervals not related to LIP area in the tropics cannot be rejected.}}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

>>>>

\section*{TABLES}

\begin{table}[h!]
\scriptsize
\caption{place holder}
\noindent\makebox[\textwidth]{
\begin{tabular}{c c c c c}
\hline
\textbf{Fraction} & \textbf{$^{206}$Pb/$^{238}$U} & & \textbf{$^{207}$Pb/$^{235}$U} & \\
& \textbf{Age [Ma]} & $\pm$2$\sigma$ & \textbf{Age [Ma]} & $\pm$2$\sigma$ \\
\hline
z1 & 823.2201669 & 1.067507326 & 823.4322744 & 2.609783978 \\
z2 & 822.401975 & 0.714471249 & 819.0720505 & 1.260737 \\
z4 & 836.2094848& 1.478314118 & 828.1995093 & 6.104877613 \\
z5 & 834.109136 & 1.288954576 & 825.9918302 & 5.720788585 \\
z16 & 831.1612867 & 0.741238812 & 832.226412 & 1.64433912 \\
z17 & 854.9767495 & 0.72532716 & 855.8348689 & 1.16873047 \\
z18 & 812.4046191 & 0.665110984 & 818.3985038 & 1.082055988 \\
z19 & 832.8963617 & 0.694437022 & 833.1583004 & 1.060745556 \\
\hline
\end{tabular}
}
\begin{tablenotes}[para,flushleft]
place holder.
\end{tablenotes}
\label{tab:LIPs}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/LIP_Map.pdf}
	\caption{Map of current extent of volcanic lithologies associated with LIPs that erupted between 520~Ma and the present as well as the estimates of the initial LIP area used in the area analysis (modified slightly from \citealp{Ernst2017a}).}
	\label{fig:LIP_map}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{LIP preservation through time. The ratio of estimates of the present-day area to that of the original area are shown for 19 basaltic LIPs. An exponential fit is made to the 13 basaltic LIPs that have not been buried after emplacement, which yields a half-life of $\sim$36~Myr.}
	\label{fig:LIP_preservation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A)} Paleolatitude of emplacement (centroid) and the initial area estimate of each LIP in the compilation. \textbf{B)} Total LIP area through time for the different post-emplacement models. \textbf{C)} Tropical LIP area through time for the different post-emplacement models. The arrows indicate tropical LIP area for the ca. 720~Ma Franklin LIP and the ca. 1109~Ma Umkondo LIP. \textbf{D)} Heat map for the preferred post-emplacement model showing the latitudinal distribution of LIP area. \textbf{E)} Latitudinal extent of land ice away from the poles through time.}
	\label{fig:LIP_area}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation_cropped.pdf}
	\caption{The overlap and correlation values for various LIP post-emplacement scenarios are shown with circles (d1 : LIP decay with half-life of 36~Myr; d2: LIP decay with half-life of~120 Myr; b1: 50\% burial of LIPs associated with rifting; b2: 100\% burial of LIPs associated with rifting). These values are compared to histograms that show the range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The only scenario for which there is a positive correlation coefficient related to ice extent and LIP area is that of a relatively slow decay rate (d2) and complete burial of LIPs associated with rifting (b2). This positive correlation is weak (\textit{r}=0.10) and is not significant as randomly timed glacial intervals correlate better than the record 28\% of the time. With an associated p-value of 0.28, the null hypothesis that glacial intervals not related to LIP area in the tropics cannot be rejected.}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}
